The Socialization of Meritocracy and Market Justice Preferences at School

### 2024-07-22 01-introduction.qmd
Update edit submit
Ultimos cambios: paper, front matter, cover letter, back matter

---
author: "Equipo EDUMER"
format: html
bibliography: "input/bib/just-ineq-merit.bib"
csl: "input/bib/apa6.csl"
---

@@

In the present paper, we address the role of the perception of meritocracy on the justification of social inequalities by eighth-grade students in Chile, a country characterized by a highly stratified educational system. In particular, we focus in justifying inequalities in health, education and pensions, which are traditional social policy areas where acces to better services could be justified based on payment capacity, referred as to market justice [@lane_market_1986; @lindh_bringing_2023]. Most of the research in this realm has only considered adults, leaving aside the study of how beliefs in this field develop at student age as well as the impact of the school context and the family as the main socialization agencies [@batruch_belief_2022]. Regarding schools, the way in which they deal with unequal conditions of origin has been linked to the *hidden curriculum* [@chafel_schooling_1997], whereby students learn about distributive norms in society and mechanisms of justification of social differences.

>>>>

---
author: "Equipo EDUMER"
bibliography: "input/bib/just-ineq-merit.bib"
csl: "input/bib/multidisciplinary-digital-publishing-institute.csl"
---

@@

In the present paper, we address the role of the perception of meritocracy on the justification of social inequalities by eighth-grade students in Chile, a country characterized by a highly stratified educational system. In particular, we focus on justifying inequalities in health, education and pensions, which are traditional social policy areas where access to better services could be justified based on payment capacity, referred to as market justice [@lane_market_1986; @lindh_bringing_2023]. Most of the research in this realm has only considered adults, leaving aside the study of how beliefs in this field develop at student age as well as the impact of the school context and the family as the main socialization agencies [@batruch_belief_2022]. Regarding schools, the way in which they deal with unequal conditions of origin has been linked to the *hidden curriculum* [@chafel_schooling_1997], whereby students learn about distributive norms in society and mechanisms of justification of social differences.

### 2024-07-22 07-supplementary-material.qmd

# Supplementary Material {#appendix}

@@

## Translated items for market justice preferences

@@

kableExtra::kable(data, 
      col.names = c("English Translation", "Original Spanish"), 
      booktabs = T, escape = F, align = 'l') %>%
  kableExtra::kable_styling(latex_options = "HOLD_position", bootstrap_options = "striped", full_width = T)  %>%
  row_spec(0, bold = T)

@@

## Complete multilevel models

@@

texreg::texreg(
  l = modelos_health,
  caption = NULL,
  stars = c(0.05, 0.01, 0.001),
  custom.note = "\\item Note: Cells contain regression coefficients with standard errors in parentheses. %stars \\\\ \\item Source: own elaboration based on First Study of Civic Education 2017.",
  threeparttable = T,
  custom.model.names = paste0(rep("Model ",6), seq(0,5)),
  custom.coef.map = ccoef,
  leading.zero = TRUE,
  use.packages = FALSE,
  booktabs = TRUE,
  scalebox = 0.8,
  groups = list("Parental education (Ref.= Non-university)" = 9:10, "Socioeconomic level (Ref.= Low)" = 14:15, "Achievement score (Ref.= Low)" = 16:17, "School dependence (Ref.= Public)" = 19:20),
  custom.gof.names = c("Log Likelihood",
                       "AIC", 
                       "BIC", 
                       "Num.obs",
                       "Num. groups: Schools",
                       "Var: Schools (Intercept)"))

>>>>

# Supplementary Material

@@

# Translated items for market justice preferences

@@

kableExtra::kable(data, 
      col.names = c("English Translation", "Original Spanish"), 
      booktabs = T, escape = F, align = 'l') %>%
  kableExtra::kable_styling(latex_options = "hold_position", bootstrap_options = "striped", full_width = T)  %>%
  row_spec(0, bold = T)

@@

# Complete multilevel models

@@

texreg::texreg(
  l = modelos_health,
  caption = NULL,
  stars = c(0.05, 0.01, 0.001),
  custom.note = "\\item Note: Cells contain regression coefficients with standard errors in parentheses. %stars \\\\ \\item Source: own elaboration based on First Study of Civic Education 2017.",
  threeparttable = T,
  custom.model.names = paste0(rep("Model ",6), seq(0,5)),
  custom.coef.map = ccoef,
  leading.zero = TRUE,
  use.packages = FALSE,
  booktabs = TRUE,
  scalebox = 0.7,
  groups = list("Parental education (Ref.= Non-university)" = 9:10, "Socioeconomic level (Ref.= Low)" = 14:15, "Achievement score (Ref.= Low)" = 16:17, "School dependence (Ref.= Public)" = 19:20),
  custom.gof.names = c("Log Likelihood",
                       "AIC", 
                       "BIC", 
                       "Num.obs",
                       "Num. groups: Schools",
                       "Var: Schools (Intercept)"))

### 2024-07-22 back_matter.qmd

---
title: "The Socialization of Meritocracy and Market Justice Preferences at School"
subtitle: "Back Matter"
format:
  hikmah-pdf: 
    indent: false
  hikmah-manuscript-pdf: 
    indent: false
bibliography: "input/bib/just-ineq-merit.bib"
csl: "input/bib/apa6.csl"
link-citations: true
linestretch: 1.15       
mainfont: Times New Roman
fontsize: 12pt          
geometry: "left=2.54cm,right=2.54cm,top=2.54cm,bottom=2.54cm"
papersize: letter
colorlinks: true
fig-height: 4
fig-width: 7.5
header-includes:
  - \usepackage{threeparttable}
---

## Acknowledgments

@@

## Authors' Contributions

The following statements should be used "Conceptualization, X.X. and Y.Y.; Methodology, X.X.; Software, X.X.; Validation, X.X., Y.Y. and Z.Z.; Formal Analysis, X.X.; Investigation, X.X.; Resources, X.X.; Data Curation, X.X.; Writing – Original Draft Preparation, X.X.; Writing – Review & Editing, X.X.; Visualization, X.X.; Supervision, X.X.; Project Administration, X.X.; Funding Acquisition, Y.Y.”

## Conflict of Interest

@@

## Funding

@@

## Data Avaibility Statement

@@

## References

>>>>

---
title: "The Socialization of Meritocracy and Market Justice Preferences at School"
subtitle: "Back Matter"
format:
  hikmah-pdf: 
    indent: false
  hikmah-manuscript-pdf: 
    indent: false
bibliography: "input/bib/just-ineq-merit.bib"
csl: "input/bib/multidisciplinary-digital-publishing-institute.csl"
link-citations: true
linestretch: 1.15       
mainfont: Times New Roman
fontsize: 12pt          
geometry: "left=2.54cm,right=2.54cm,top=2.54cm,bottom=2.54cm"
papersize: letter
colorlinks: true
fig-height: 4
fig-width: 7.5
header-includes:
  - \usepackage{threeparttable}
---

# Acknowledgments

@@

# Authors' Contributions

Conceptualization, Juan Carlos Castillo & Mauricio Salgado; Methodology, Juan Carlos Castillo, Kevin Carrasco & Andreas Laffert; Software, Kevin Carrasco & Andreas Laffert; Formal Analysis, Kevin Carrasco & Andreas Laffert; Writing – Original Draft Preparation, Juan Carlos Castillo, Mauricio Salgado, Kevin Carrasco & Andreas Laffert; Visualization, Kevin Carrasco & Andreas Laffert; Supervision, Juan Carlos Castillo.

# Conflict of Interest

@@

# Funding

@@

# Data Avaibility Statement

@@

{{< pagebreak >}}
